Solar jet observed at the limb in SDO/SST

### 2016-05-11 paper/ms_temp_paper.tex
Stero fig bugs

multi = texfigure.MultiFigure(2, 2, reference="stereo")

@@

	amap = sunpy.map.Map(im)
	crop = amap.submap([-640, -510]*u.arcsec, [-430, -300]*u.arcsec)

	Fig1 = manager.save_figure('stereo{}'.format(i+1), fig)
	Fig1.subfig_width = r"0.25\textwidth"
	Fig1.caption = ""
	multi.append(Fig1)

multi.placement = 't'
multi.caption = ""
\end{pycode}

\py[STEREO]||

>>>>

multi_ST = texfigure.MultiFigure(1, 4, reference="stereo")

@@

	amap = sunpy.map.Map(im)
	crop = amap.submap([-640, -510]*u.arcsec, [-430, -330]*u.arcsec)
	crop.plot(title=False)
	Fig1 = manager.save_figure('stereo{}'.format(i+1), fig)
	Fig1.subfig_width = r"0.2\textwidth"
	Fig1.caption = ""
	multi_ST.append(Fig1)

multi_ST.placement = 't'
multi_ST.caption = "EUVI $30.4$ nm images from STEREO on $21$st June at a) 07:26:15, b) 07:36:15, c) 07:46:15 and d) 07:56:15. "
\end{pycode}

\py[STEREO]|multi_ST|
